Verifying Demonstrations

### 2020-03-13 paper/intro.tex
Edits intro: contributions and outline

The first (and second) contribution enables us to do \ac{DB} \ac{ABC}.
The third enables us also to do \ac{DB} \ac{ABC}, just without \ac{DBTF} 
resistance.

Our main contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} 
for \ac{DB}, but which is different from that of \textcite{DistanceBounding} or 
\textcite{Bussard-Bagga} (DBPK-Log).
Our adaptation fulfills all the requirements for modern \ac{DB} protocols, 
including \ac{DBDH} (which was an attack against the original protocol of 
Brands and Chaum) and \ac{DBTF}.
More importantly, it is public-key\footnote{%
  The majority of published works are in the shared-key setting.
  However, both the protocol by \textcite{DistanceBounding} and that of 
  \textcite{Bussard-Bagga} are public key.
}, handles malicious impersonating verifiers.
Since it is based on the Schnorr protocol, it provides a distance-bounded 
\ac{PK} for discrete logarithms.
That allows us to replace the plain Schnorr protocol in \acp{ZKPK} with our 
distance-bounding version and thus make general privacy-preserving, 
attribute-based credential systems distance bounding.

@@

The paper is organized as follows.
\Cref{system-model}, we describe our system model and summarize the desired 
properties 
We then discuss related work in terms of these properties in 
\cref{related-work}, and in \cref{building-blocks}, we give 
the relevant background on the building blocks of our solution.

\Cref{DB-Schnorr-UWB}, we present a new \ac{DB} version of the Schnorr protocol, 
different from that originally proposed by \textcite{DistanceBounding}.
We provide a proof of its security and formally verify it using 
Tamarin~\cite{TamarinDB}.

We analyze its security in \cref{SecurityAnalysis} and estimate its performance 
in \cref{PerformanceAnalysis}.

Finally, we discuss our assumptions and results in \cref{Discussion} and give 
our conclusions in \cref{Conclusion}.

>>>>

The first (and second) contribution enables us to do distance-bounding 
privacy-preserving attribute-based credentials based on discrete logarithms, 
\eg~\cite{Camenisch-phdthesis} and~\cite{CLsignatures}.
To our knowledge, no other distance-bounding protocol achieves this.
The third contribution (bit-by-bit version) also enables us to do the same, 
just without \ac{DBTF} resistance.

@@

The paper is organized as follows.
\Cref{Preliminaries} introduces the preliminaries of \ac{ZKPK} and \ac{DB}.
\Cref{DB-Schnorr} introduces the first version, where we assume that we can 
send all bits at the same time.
\Cref{DB-Schnorr-PKI} introduces the \ac{PKI} and \ac{AKE} to use the first 
version of the protocol in practice.
\Cref{DB-Schnorr-nbit} describes the bit-by-bit version of the protocol.
Finally, we conclude with a discussion of our results in \cref{Conclusion}.
